Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-19 docs/paper/paper.Rmd
add metadata extraction and summary statistic generation

# Load ECDC forecast metadata. See data-raw/get-hub-metadata.R for munging
#metadata <- fread(here("data", "forecast-metadata.csv"))

@@

  We extracted forecasts and data on notified weekly COVID-19 cases from the ECDC forecasting hub from XX to the XX for the ensemble model (referenced as `EuroCOVIDhub-ensemble` by the hub team) and the surrogate model (submitted as `epiforecasts-weeklygrowth`).
  We included all locations covered by the ECDC forecasting hub which were 32 European countries, including all countries of the European Union and European Free Trade Area, and the United Kingdom.
  Data on notified weekly cases was originally sourced from the Johns Hopkins University curated data repository (JHU, [@REF]).
  We used the latest available observed data. As observations are subject to revisions this means that the data used to produce forecasts for a given date may not reflect the data used for evaluation.
  The follows the common practice of the forecasting hub projects in treating the latest available data as the forecast target regardless of the number of data revisions.
  Incidence was aggregated over the Morbidity and Mortality Weekly Report (MMWR) epidemiological week definition of Sunday through Saturday.

@@

@@

- Date range of forecasts
- Forecasts per country
- Total number of forecast models and average per location and per forecast date
- Summarises general trends in incidence in the data

>>>>

# Load forecast metedata. See data-raw/get-hub-metadata.R for munging
metadata <- fread(here("data", "metadata.R"))

@@

  We extracted forecasts and data on notified weekly COVID-19 cases from the ECDC forecasting hub from 15th of January 2022 to the 19th of July 2022 for the ensemble model (referenced as `EuroCOVIDhub-ensemble` by the hub team) and the surrogate model (submitted as `epiforecasts-weeklygrowth`).
  We included all locations covered by the ECDC forecasting hub which were 32 European countries, including all countries of the European Union and European Free Trade Area, and the United Kingdom.
  Data on notified weekly cases was originally sourced from the Johns Hopkins University curated data repository (JHU, [@REF]).
  We used the latest available observed data. As observations are subject to revisions this means that the data used to produce forecasts for a given date may not reflect the data used for evaluation.
  The follows the common practice of the forecasting hub projects in treating the latest available data as the forecast target regardless of the number of data revisions.
  Incidence was aggregated over the Morbidity and Mortality Weekly Report (MMWR) epidemiological week definition of Sunday through Saturday.

@@

```{r metadata}
# Number of locations
locations <- metadata |>
  DT(, location) |>
  unique() |>
  length()

# Number of models overall
models <- metadata |>
  DT(, model) |>
  unique() |>
  length()

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "forecast_date")

# Models per location
models_per_location <- metadata |>
  summarise_forecasts_by(by = "location")

# Models with a single location target
locations_per_model <- metadata |>
  summarise_forecasts_by(var = "location", by = "model")

# Single target models per location
single_locs_models_per_loc <- metadata |>
  DT(locations_per_model[n == 1], on = "model") |>
  summarise_forecasts_by(by = "location")

# Global models
global_models <- locations_per_model |>
  DT(n > 30) |>
  DT(, model)

# Partial coverage models
partial_coverage <- locations_per_model |>
  DT(n > 1) |>
  DT(n <= 30)

# Models coverage of forecast datees
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "forecast_date", by = "model") |>
  DT(order(n))
```

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK). 
- Date range of forecasts
- Forecasts per country
- Total number of forecast models and average per location and per forecast date
- Summarises general trends in incidence in the data
